Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-05-30 outputs/paper/paper.qmd
Added ggplot2 and ggspatial packages and began writing code to map the locations of subdivisions

## Load packages
library(tidyverse)
library(knitr)
library(here)
library(sf)

@@

>>>>

## Load packages
library(tidyverse)
library(knitr)
library(here)
library(sf)
library(ggplot2)
library(ggspatial)

@@

### Results

# code referenced from: https://sharlagelfand.github.io/opendatatoronto/articles/articles/spatial_data.html
cleaned_voting_locations |>
  c("address_full", "geometry")
ggplot() +
  geom_sf(data = address) +
  geom_sf(data = geometry) +
  theme_void()
